Turbulence in compact to giant HII regions

### 2022-08-12 strucfunc_paper.tex
Re-order subsections in discussion

\begin{figure*}
 \centering
 \includegraphics[width=\linewidth]{Figures/model-strucfunc-annotated}\par
 \caption{
   Example of the model structure function for homogeneous fluctuations,
   together with a realization of the corresponding velocity field
   on a \(512 \times 512\) pixel grid.  
   (a)~Idealized structure function (blue line)
   for the parameters \(m = 1\) and \(r_0 = \SI{64}{pixels}\).
   Red and green lines show the effects of observational limitations
   at small scales (seeing and noise)
   and at large scales (finite-map effects).
   (b)~Examples of inhomogeneous effects at large scales,
   which are not included in the model structure function.
 }
 \label{fig:model-strucfunc}
\end{figure*}

@@

\input{Corr}

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/corr-svsL}
\caption{
  The relationship between plane-of-sky velocity dispersion,
  \(\log_{10} \sigma\pos\),
  and \hii{} region luminosity,
  \(\log_{10} L(\ha)\),
  derived from our results.
  The markers indicates Galactic (triangles),
  Magellanic (squares) and extragalactic (circles) regions.
  The black solid line is the median linear regression,
  with thin red lines showing 400 random samples from the posterior
  distribution to indicate the uncertainty in the regression.}
\label{fig:sigvsl}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/corr-rvsS}
\caption{
  As Figure~\ref{fig:sigvsl} but for the relationship between
  correlation length of velocity fluctuations,
  \(\log_{10} r_0\),
  and  \hii{} region diameter,
  \(\log_{10} D_{\hii}\).}
\label{fig:rvsR}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/corr-los-vs-pos}
\caption{
  As Figure~\ref{fig:sigvsl} but for the relationship between
  line-of-sight non-thermal velocity dispersion,
  \(\sigma\los\),
  and plane-of-sky velocity dispersion,
  \(\sigma\pos\).
  The dashed line shows the the linear fit obtained by
  \citet{2011MNRAS.413..705L} for a sample of
  small-to-intermediate size \hii{} regions in the M33 galaxy. 
}
\label{fig:los-vs-pos}
\end{figure}

>>>>

\begin{figure*}
 \centering
 \includegraphics[width=\linewidth]{Figures/model-strucfunc-annotated}\par
 \caption{
   Example of the model structure function for homogeneous fluctuations,
   together with a realization of the corresponding velocity field
   on a \(512 \times 512\) pixel grid.  
   (a)~Idealized structure function (blue line)
   for the parameters \(m = 1\) and \(r_0 = \SI{64}{pixels}\).
   Red and green lines show the effects of observational limitations
   at small scales due to seeing and noise.
   (b)~Examples of inhomogeneous effects at large scales,
   which are not included in the model structure function.
 }
 \label{fig:model-strucfunc}
\end{figure*}

@@

\input{Corr}
\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/corr-los-vs-pos}
\caption{
  The relationship between 
  line-of-sight non-thermal velocity dispersion,
  \(\sigma\los\),
  and plane-of-sky dispersion of velocity centroids,
  \(\sigma\pos\)
  derived from our results.
  Symbols indicate Galactic (triangles),
  Magellanic (squares) and extragalactic (circles) regions.
  The black solid line is the median linear regression,
  with thin red lines showing 400 random samples from the posterior
  distribution to indicate the uncertainty in the regression.  
  The dashed line shows the the linear fit obtained by
  \citet{2011MNRAS.413..705L} for a sample of
  small-to-intermediate size \hii{} regions in the M33 galaxy. 
}
\label{fig:los-vs-pos}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/corr-svsL}
\caption{
  The relationship between
  plane-of-sky dispersion of velocity centroids,
  \(\log_{10} \sigma\pos\),
  and \hii{} region luminosity,
  \(\log_{10} L(\ha)\),
  derived from our results.
  Symbols and line types are as in Figure~\ref{fig:sigvsl}. 
}
\label{fig:sigvsl}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/corr-rvsS}
\caption{
  The relationship between
  correlation length of velocity fluctuations,
  \(\log_{10} r_0\),
  and  \hii{} region diameter,
  \(\log_{10} D_{\hii}\)
  derived from our results.
  Symbols and line types are as in Figure~\ref{fig:sigvsl}. 
}
\label{fig:rvsR}
\end{figure}
